# Dissertation Process {#dissertation}

The graduate school has a general dissertation process, so we could follow their guidelines. However, it would be helpful to spell out our own logistics for dates, committee assemblage, proposal process, and links within the I/O document so students can reference this if they have questions. Further, I put the general dissertation process outline in the PAD which can be reviewed and expanded upon with more specific procedural details. Below are some examples of programs which have their dissertation process spelt out. 

+ [Chattanooga](https://www.utc.edu/doctorate-learning-leadership/doctoralguide/dissertationprocess/finaldefense.php)
+ [Louisiana State](https://www.lsu.edu/hss/psychology/grad/io_graduate_handbook_2019-11-07.pdf)

The below is taken from Renata's dissertation - an outline of important dates (AYs 20-22)

```{r Spring2021, echo=FALSE, warning=FALSE}
# Forms for Dissertation found here: 
##https://www.montclair.edu/graduate/current-students/doctoral-students/


## https://www.rdocumentation.org/packages/TeachingDemos/versions/2.10/topics/cal

library(TeachingDemos)

## Colors in 8 digit hex: https://www.quackit.com/css/color/values/css_hex_color_notation_8_digits.cfm


setday <- cal(1,2021) 
setday <- cal(2,2021)
setday(1)
text(0.5,0.5,"Form\nDissertation\nCommittee")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday <- cal(3,2021)                               
setday <- cal(4,2021)
setday(1)
text(0.5,0.5,"Defend\n proposal")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday <- cal(5,2021)                              
setday <- cal(6,2021)
setday <- cal(7,2021)
setday <- cal(8,2021)

setday <-cal(9,2021)
setday(1)
text(0.5,0.5,"Have proposal\nready")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday(25)
text(0.5,0.5,"Proposal approval\nform to\nGradschool")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday <-cal(10,2021)
setday <-cal(11,2021)
setday <-cal(12,2021)

```


```{r Spring2022, echo=FALSE, warning=FALSE}

setday <-cal(1,2022)

setday <-cal(2,2022)

setday <-cal(3,2022)
setday(1)
text(0.5,0.5,"Defense date\nsubmitted to\nGradschool")
rect(-0.04,-0.04,1.04,1.04, col="#ff000066")

setday <-cal(4,2022)
setday(1)
text(0.5,0.5,"Defend dissertation\nby this date")
rect(-0.04,-0.04,1.04,1.04, col="#ff000066")

setday(2)
text(0.5,0.5,"Submit Approval\nto Gradschool")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday <-cal(5,2022)

```